Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-20 lloveras_2020.tex
cambiando cosas

\begin{equation}\label{Er}
E_r = \int\,\textrm{d}T\,T\,\LDEM(T)\,\Lambda(T)
\end{equation}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

>>>>

\begin{equation}\label{Er}
E_r = \int\,\textrm{d}T\,\LDEM(T)\,\Lambda(T)
\end{equation}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of type I (blue), II (red), and III (green), for CR-2082 (top panel) and CR-2208 (bottom panel). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, analyzed a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively.
